Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-26 paper/paper.tex
Add to results of rating-based method.

>>>>

The green curve in the upper panel of Fig. \ref{fig:MSE_SimR} is the MSE of
$LinRegSim$, which was already shown in Fig. \ref{fig:Linear}, and is included
here for comparison.  $LinRegSim$ outperforms always-guessing-the-average for
all $n > 2$ and does better than $PearSim$ over the entire scope of the plot.
$UserPredSim$ is shown in blue and for $3 < n < 33$ achieves a lower MSE than
$LinRegSim$.

The lower panel of Fig. \ref{fig:MSE_SimR} shows the MSE of estimators in the
experiment carried out with item pairs with $N \geq 80$. The curves for
$PearSim$, always guessing the average, and $LinRegSim$ exhibit behavior
analogous to that observed in the $N \geq 40$ experiment, with addition of
increased noise. The performance of $UserPredSim$, meanwhile, is significantly
improved, achieving the MSE that $PearSim$ reaches at $n \approx 70$ by $n
\approx 20$. This result demonstrates the efficacy, at least in some datasets,
of measuring and exploiting {\em user predictivity} when estimating item-item
similarity.

Next, we consider the results of using $UserPredSim$ to estimate $TrueSimPref$.
